% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

%I would like to appreciate my thesis supervisor Prof. Dr Marlon Dumas, for the supervision, support, and guidance he has given to me during a whole academic year. It would not have been achievable for me to defend if it was not by his advice and help. He always had the patience to listen to my thoughts, give productive feedback and, direct me in the correct path whenever I wanted it the most. I am additionally extremely grateful for the various opportunities he gave me, where I obtained several research experiences, learned around several exciting topics in the area of Process Mining.  

%I would further like to show my deep appreciation to my parents for their love, unlimited help, and encouragement during all times of my life. Lastly, I dedicate my work to the memory of Prof. Dr Sherif Sakr, who continuously believed in my strength to be successful in the academic field.

I would like to appreciate my thesis supervisor Prof. Dr Marlon Dumas, for the supervision, support, and guidance he has given to me during a whole academic year. It would not have been achievable for me to defend if it was not by his advice and help. He always had the patience to listen to my thoughts, give productive feedback and, direct me in the correct path whenever I wanted it the most. I am additionally extremely grateful for the various opportunities he gave me, where I obtained several research experiences, learned around several exciting topics in the area of Process Mining. \\


Besides my supervisor, I would like to thank the University of Tartu, Institute of Computer Science, which gave me the opportunity to study the master degree in data science. Additionally, My sincere thanks also go to Prof. Dr Salwa Nassar from Electronics Research Institue, Egypt, who continuously believed in my strength with lots of support, encourage, and guidance.  
\\

I would further like to show my deep appreciation to my parents, and family for their love, unlimited help, and encouragement during all times of my life. Lastly, I dedicate my work to the memory of Prof. Dr Sherif Sakr, who continuously believed in my strength to be successful in the academic field.



\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------


